---
title: "Statistics in R"
author: Quanyuan He
output: html_notebook
params:
  doc_title:"statisitc_in_r"
---

## Section 1: General libraries for statistic analysis:
### Premodeling stage
Data visualization: ggplot2, matplotlib, seabean, googleVis
Data transformation: plyr, data.table
Missing value imputations: MissForest, MissMDA
Outline Detection: Outliers, EVIR
Feature Selection: Features, RRF
Dimension Reduction: FactoMineR, CCP

### Modeling Stage
Continuous Regression: car, randomforest
Ordinal Regression: RMiner, CoreLearn
Classification: Caret, BigRF
Clustering: CBA, BankCluster
Time Series: forest, LTSA
Survival: survival, Basta

### Post Modeling Stage
General Model Validation: LSMeans, Comparison
Regression Validation: RegTest, ACD
Classfication Validation: BinomTools, DAIM
Clustering Validation: ClustEval, SigClust
ROC Analysis: PROC, TimeROC

### Others
Improve performance: Rcpp, parallel
Work with web: XML, jasonlit, httr
Report results: shiny, RMarkdown
Text Mining: tm, twitterR
Database:sqldf, RODBC, RMongo
Miscellaneous: swirl, reshape2, qcc

### References

\newpage

## Test Data Sources in R

```{r}
data()
# List the data sets available in package 'MASS'
data(package = "MASS")
```

## Distributions and Random

```{r, eval = FALSE}
## Generate a vector of (10) normal random variables with a mean of 0, (10) uniformed variables with mean of 0 and (10)

x <- c(rnorm(n=10, mean = 2, sd = 2), runif(n=10, min=0, max=10))
col1 <- runif(12^4, 0, 2)
col2 <- rnorm(12^4, 0, 2)
col3 <- rpois(12^4, 3)
col4 <- rchisq(12^4, 2)
```

## Generalized Linear Models
```{r, results="hide"}
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
group <- gl(2, 10, 20, labels = c("Ctl","Trt"))
weight <- c(ctl, trt)
print(weight)
print(group)
lm.D9 <- lm(weight ~ group)
lm.D90 <- lm(weight ~ group - 1) # omitting intercept
# }
# NOT RUN {
anova(lm.D9)
summary(lm.D90)
# }
# NOT RUN {
opar <- par(mfrow = c(2,2), oma = c(0, 0, 1.1, 0))
plot(lm.D9, las = 1)      # Residuals, Fitted, ...
par(opar)
# }
```


## Power Analysis
* Our null hypothesis is that the coin is fair and lands heads 50% of the time (
π = 0.50).
* Our alternative hypothesis is that the coin is loaded to land heads more then 50% of the time (
π > 0.50). 
* Question: How many times should we flip the coin to have a high probability (or power), say 0.80, of correctly rejecting the null ofπ= 0.5 if our coin is indeed loaded to land heads 75% of the time?
```{r, eval=FALSE}
# Power analysis (pwr) package  is used for power analysis in R
library(pwr)
p.out <- pwr.p.test(h = ES.h(p1 = 0.75, p2 = 0.50),
           sig.level = 0.05,
           power = 0.80,
           alternative = "greater")
plot(p.out)
```
# Maximum likelihood fitting of univariate distribution in MASS package
```{r}
library(MASS)
set.seed(123)
x <- rgamma(100, shape = 5, rate = 0.1)
fitdistr(x, "gamma")
fitdistr(x, dgamma, list(shape = 1, rate = 0.1), lower = 0.001)

set.seed(123)
x3 <- rweibull(100, shape = 4, scale = 100)
fitdistr(x3, "weibull")

set.seed(123)
x4 <- rnegbin(500, mu = 5, theta = 4)
fitdistr(x4, "Negative Binomial")
options(op)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

